Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-02-21 Paper.tex
Added ref command to unflagged occurance of 'TBD' in relation to "homestead block number"
Added new command for referencing "firsthomesteadblock" number
Removed incorrect appearance of 'floor' operator on secp256k1n div 2 in eq. 207
Corrected range brackets on signature variable 'r'

The canonical difficulty of a block of header $H$ is defined as $D(H)$:
\begin{equation}
D(H) \equiv \begin{cases}
131072 & \text{if} \quad H_i = 0\\
{P(H)_H}_d + \left\lfloor\frac{{P(H)_H}_d}{2048}\right\rfloor & \text{if} \quad H_s < {P(H)_H}_s + 13\\
\max \{ 131072, x \} & \text{otherwise}\\
\end{cases}
\end{equation}
where:
\begin{equation}
x = {P(H)_H}_d - \left\lfloor\frac{{P(H)_H}_d}{2048}\right\rfloor
\end{equation}

@@

It is assumed that the sender has a valid private key $p_r$, which is a randomly selected positive integer (represented as a byte array of length 32 in big-endian form) in the range \hbox{$(1, \mathtt{\tiny secp256k1n} - 1)$}.

@@

We declare that a signature is invalid unless all the following conditions are true:
\begin{align}
0 < r &< \mathtt{\tiny secp256k1n} \\
0 < s &< \begin{dcases}
\hphantom{\lfloor} \mathtt{\tiny secp256k1n} & \text{if} \quad H_i < \firsthomesteadblock \\
\left\lfloor \mathtt{\tiny secp256k1n} \div 2 \right\rfloor & \text{otherwise} \\
\end{dcases} \\
 v &\in \{27,28\} 
\end{align}
where:
\begin{align}
\mathtt{\tiny secp256k1n} &= 115792089237316195423570985008687907852837564279074904382605163141518161494337
%\mathtt{\tiny secp256k1p} &= 2^{256} - 2^{32} - 977\\
\end{align}

>>>>

\newcommand{\mindifficulty}{D_0}
\newcommand{\frontiermod}{\ensuremath{\varsigma_1}}
\newcommand{\homesteadmod}{\ensuremath{\varsigma_2}}
\newcommand{\expdiffsymb}{\ensuremath{\epsilon}}
\newcommand{\diffadjustment}{x}

The canonical difficulty of a block of header $H$ is defined as $D(H)$:
\begin{equation}
D(H) \equiv \begin{dcases}
\mindifficulty & \text{if} \quad H_i = 0\\
\text{max}\!\left(\mindifficulty, {P(H)_H}_d + \diffadjustment\times\frontiermod + \expdiffsymb \right) & \text{if} \quad H_i<\firsthomesteadblock\\
\text{max}\!\left(\mindifficulty, {P(H)_H}_d + \diffadjustment\times\homesteadmod + \expdiffsymb \right) & \text{otherwise}\\
\end{dcases}
\end{equation}
where:
\begin{equation}
\mindifficulty \equiv 131072
\end{equation}
\begin{equation}
\diffadjustment \equiv \left\lfloor\frac{{P(H)_H}_d}{2048}\right\rfloor
\end{equation}
\begin{equation}
\frontiermod \equiv \begin{cases}
1 & \text{if} \quad H_s < {P(H)_H}_s + 13 \\
-1 & \text{otherwise} \\
\end{cases}
\end{equation}
\begin{equation}
\homesteadmod \equiv \text{max}\left( 1 - \left\lfloor\frac{H_s - {P(H)_H}_s}{10}\right\rfloor, -99 \right)
\end{equation}
\begin{equation}
\expdiffsymb \equiv \left\lfloor 2^{ \left\lfloor H_i \div 100000 \right\rfloor - 2 } \right\rfloor
\end{equation}

@@

It is assumed that the sender has a valid private key $p_r$, which is a randomly selected positive integer (represented as a byte array of length 32 in big-endian form) in the range \hbox{$[1, \mathtt{\tiny secp256k1n} - 1]$}.

@@

We declare that a signature is invalid unless all the following conditions are true:
\begin{align}
0 < r &< \mathtt{\tiny secp256k1n} \\
0 < s &< \begin{dcases}
\mathtt{\tiny secp256k1n} & \text{if} \quad H_i < \firsthomesteadblock \\
\mathtt{\tiny secp256k1n} \div 2 & \text{otherwise} \\
\end{dcases} \\
 v &\in \{27,28\} 
\end{align}
where:
\begin{align}
\mathtt{\tiny secp256k1n} &= 115792089237316195423570985008687907852837564279074904382605163141518161494337
%\mathtt{\tiny secp256k1p} &= 2^{256} - 2^{32} - 977\\
\end{align}
